### 2022-09-22 Paper.tex
Initial Overleaf Import

\documentclass{article}
\usepackage[utf8]{inputenc}
\title{Foreign Aid Choices and Effects}
\author{Nicholas Ray}
\date{September 2022}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools,amssymb,amsthm}
\usepackage{setspace}
\doublespacing
\usepackage[backend=biber, style=authoryear, maxbibnames=99]{biblatex}
\renewbibmacro{in:}{}
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}
  \setunit*{\addnbthinspace}
  \printfield{number}
  \setunit{\addcomma\space}
  \printfield{eid}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\AtEveryBibitem{
  \clearfield{issn}
  \clearfield{month}
  \clearfield{urlyear}
  \clearlist{language}
  \clearfield{note}
  \ifentrytype{online}{}{
    \clearfield{url}
  }
}
\addbibresource{References.bib}
\begin{document}
\maketitle
\section*{What needs to be explained} 
Developing countries seem to have an increased ability to choose donors for foreign aid. Not only has China been giving an incredible amount of aid, but now the U.S. and G7 are expanding their aid opportunities. Given this phenomenon, how do aid-seeking countries decide between bilateral donors and international institutions like the IMF and World Bank? And, how does choosing Chinese money over IMF funds, for instance, affect the politics of the recipient country? In other words, what is the political difference between receiving money from international organizations and other entities, like the U.S. or China? Is the BRI really an attractive substitute for IMF funding?

\section*{Theory} 
Given that there are more than one donors offering money, recipients pick the sum that maximizes their utility. Their utility function has two parameters: net value of the sum minus the cost of concessions to the donor. Assumption: 1) donors have strategic interests that define who they give money to 2) democratic countries and international institutions have weakly democratic strategic aims whereas autocratic donors have weakly autocratic aims.

One period game. Competition when more than one donor present, where recipient can choosing between IMF loan and investment from other countries. Countries compete by offering more money or lowering concessions required. What about reneging? (recipients less likely to renege when donor matches their policy preference as concessions are lower? Or reputation loss and inability to get future monies?)  Implications being that countries have had to make less concessions over time due to competition and tend to accept money from donors with similar preferences, if available.

\textbf{Expected Implications} 
\begin{align*}
    H_1:\; &\text{Autocratic recipients choose to rather receive money from autocratic donors than}\\
    &\text{international organizations or democratic donors.}\\
    H_2:\; &\text{Recipients of (democratic) autocratic aid will become weakly more (democratic) autocratic.}
\end{align*}

\section*{Alternative Explanations}

\section*{Methodology}
Some descriptive stats on foreign aid spending by country and organization over time.

Test: Look at countries who previously received IMF funding who switched to Chinese money, use it as treatment?

\section*{Complications}

\printbibliography
\end{document}

### 2022-09-26 Paper.tex
New thoughts on deglobalization

@@
 \section*{What needs to be explained}
+Given the seeming consensus of economic and political deglobalization,  namely in the West, there is attention being paid to China's position in this story, whether as a cause or of an effect.
+Regardless, I argue that China's eminence in the foreign aid spending decreases donor competition for foreign aid and leads to a reduction in perceived concessions on behalf of the recipient.
+Further, autocratic countries are likely to disproportionately benefit from this concession deficit and thus work more with China than democracies.
+Can I formalize this?
+------
+
 Developing countries seem to have an increased ability to choose donors for foreign aid.

### 2022-10-04 Extra.tex
progress

--- 2022-09-26 Paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-\title{Foreign Aid Choices and Effects}
-\author{Nicholas Ray}
-\date{September 2022}
-\usepackage[margin=1in]{geometry}
-\usepackage{mathtools,amssymb,amsthm}
-\usepackage{setspace}
-\doublespacing
-\usepackage[backend=biber, style=authoryear, maxbibnames=99]{biblatex}
-\renewbibmacro{in:}{}
-\renewbibmacro*{volume+number+eid}{%
-  \printfield{volume}
-  \setunit*{\addnbthinspace}
-  \printfield{number}
-  \setunit{\addcomma\space}
-  \printfield{eid}}
-\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
-\AtEveryBibitem{
-  \clearfield{issn}
-  \clearfield{month}
-  \clearfield{urlyear}
-  \clearlist{language}
-  \clearfield{note}
-  \ifentrytype{online}{}{
-    \clearfield{url}
-  }
-}
-\addbibresource{References.bib}
-\begin{document}
-\maketitle
 \section*{What needs to be explained}
 Given the seeming consensus of economic and political deglobalization,  namely in the West, there is attention being paid to China's position in this story, whether as a cause or of an effect.
-Regardless, I argue that China's eminence in the foreign aid spending decreases donor competition for foreign aid and leads to a reduction in perceived concessions on behalf of the recipient.
-Further, autocratic countries are likely to disproportionately benefit from this concession deficit and thus work more with China than democracies.
+Regardless, I argue that China's eminence in the foreign aid spending increases donor competition for foreign aid and leads to a reduction in perceived concessions on behalf of the recipient.
+Further, autocratic countries are likely to disproportionately benefit from this concession deficit and thus work more with China more than democracies.
 Can I formalize this?
+
+Differences between money flows: aid (grants) versus loans (debt) and official da (ODA) and (OOF) (ODA like flows less economically self-interested, Dreher?)
 ------
@@
 \section*{Complications}
-
-\printbibliography
-\end{document}

### 2022-10-04 Paper.tex
Aid flow types
progress

--- 2022-09-22 Paper.tex
@@
 \usepackage[utf8]{inputenc}
-\title{Foreign Aid Choices and Effects}
+\title{\vspace{-2.75cm}634\vspace{-0.5cm}}
 \author{Nicholas Ray}
-\date{September 2022}
+\date{\vspace{-0.30cm}October 31 2022\vspace{-1cm}}
 \usepackage[margin=1in]{geometry}
@@
 \doublespacing
-\usepackage[backend=biber, style=authoryear, maxbibnames=99]{biblatex}
+\usepackage[backend=biber, style=authoryear, maxbibnames=99, uniquelist=false]{biblatex}
 \renewbibmacro{in:}{}
@@
 }
-\addbibresource{References.bib}
+\addbibresource{ForeignAidBib.bib}
 \begin{document}
 \maketitle
-\section*{What needs to be explained} 
-Developing countries seem to have an increased ability to choose donors for foreign aid.
-Not only has China been giving an incredible amount of aid, but now the U.S.
-and G7 are expanding their aid opportunities.
-Given this phenomenon, how do aid-seeking countries decide between bilateral donors and international institutions like the IMF and World Bank?
-And, how does choosing Chinese money over IMF funds, for instance, affect the politics of the recipient country?
-In other words, what is the political difference between receiving money from international organizations and other entities, like the U.S.
-or China?
-Is the BRI really an attractive substitute for IMF funding?
+\section*{Introduction}
+%Look at Dreher's book, Kidd's international formal theory book, Hernadez 2017 paper, etc.
+BRI (\cite{dreher2022}), Globalization (papers from week 6)?
+
+Lots of academic attention on supply side provision of aid given China's entrance (e.g., \cite{dreher2018}, \cite{dreher2015}), but few explorations of the demand side after China has become a prevalent donor.
+Also research on how Chinese aid affects recipients in various ways (e.g., \cite{martorano2020}, \cite{bader2015}).
+This paper seeks to address this shortage in the literature, aiming to understand how recipient countries choose between the vast number of credible donors.
+Relevant literature: \cite{kilama2016a}, \cite{hernandez2017}, \cite{li2017a}, \cite{isaksson2018}, \cite{humphrey2019}, \cite{broich2017a}.
+
+Research Question.
+Given the literature, the decision-making of recipient countries no longer seems so trivial (i.e., why are countries choosing to receive aid money from China?).
+The literature implies that there should be a healthy mix of aid donor money given the effects shown.
+Some strategy is no involved on behalf of the recipient country; if we are not seeing a diversified diet in aid receipt, why not?
+Seems best.
 
 \section*{Theory}
-Given that there are more than one donors offering money, recipients pick the sum that maximizes their utility.
-Their utility function has two parameters: net value of the sum minus the cost of concessions to the donor.
-Assumption: 1) donors have strategic interests that define who they give money to 2) democratic countries and international institutions have weakly democratic strategic aims whereas autocratic donors have weakly autocratic aims.
-
-One period game.
-Competition when more than one donor present, where recipient can choosing between IMF loan and investment from other countries.
-Countries compete by offering more money or lowering concessions required.
-What about reneging?
-(recipients less likely to renege when donor matches their policy preference as concessions are lower?
-Or reputation loss and inability to get future monies?)  Implications being that countries have had to make less concessions over time due to competition and tend to accept money from donors with similar preferences, if available.
-
-\textbf{Expected Implications} 
-\begin{align*}
-    H_1:\; &\text{Autocratic recipients choose to rather receive money from autocratic donors than}\\
-    &\text{international organizations or democratic donors.}\\
-    H_2:\; &\text{Recipients of (democratic) autocratic aid will become weakly more (democratic) autocratic.}
-\end{align*}
-
-\section*{Alternative Explanations}
+Explanation
 
 \section*{Methodology}
-Some descriptive stats on foreign aid spending by country and organization over time.
+Data \& Variables
 
-Test: Look at countries who previously received IMF funding who switched to Chinese money, use it as treatment?
+Research Design
 
-\section*{Complications}
-
+\pagebreak
 \printbibliography

### 2022-10-25 Paper.tex
progress

@@
 \usepackage{setspace}
+\usepackage{tikz}
+\usepackage{sgame}
 \doublespacing
@@
 Given the literature, the decision-making of recipient countries no longer seems so trivial (i.e., why are countries choosing to receive aid money from China?).
-The literature implies that there should be a healthy mix of aid donor money given the effects shown.
-Some strategy is no involved on behalf of the recipient country; if we are not seeing a diversified diet in aid receipt, why not?
-Seems best.
+The literature implies that there should be a healthy mix of aid donor money given the effects shown, implying that there should be some strategy present in recipient countries.
 
 \section*{Theory}
-Explanation
+In an attempt to model the effects of having more than one donor on recipient behavior, especially when donors display heterogeneity in their loaning practices, I formalize a bargaining interaction between a recipient country and two types of donors.
+Figure 1 illustrates the extensive-form of the interaction and can be found in the appendix.
 
-\section*{Methodology}
+Bargaining occurs over two periods, with the first donor ($D_1$) making an initial loan offer ($x_1$) to the recipient ($R$).
+If the recipient accepts the loan, the first donor gets a payoff ($1-x_1$) that corresponds to the expected benefits from the conditions of the loan (e.g., political reform, trade liberalization).
+The recipient gains the value of the loan, $x_1$.
+
+If the recipient rejects the offer, then the second donor ($D_2$) has an opportunity to proffer a loan ($x_2$).
+Acceptance by the recipient in this second period yields similar payoffs to those in the first (i.e., $1-x_2$ and $x_2$), except now there are two additional parameters, $\delta$ and $\gamma$, such that the recipient's value of the loan in the second period totals to $\delta \gamma x_2$.
+Consequently, the donor would receive $1-\delta \gamma x_2$ if the offer is accepted.
+
+The parameter $\delta$ commonly appears in multi-period bargaining models and is referred to as a discount factor.
+The substantive interpretation in this scenario is that recipients shopping for loans have some time sensitive reason for wanting a loan, such as an economic crisis.
+The smaller that $\delta$ is, the more harmful it is for recipients to refuse the first loan offer they receive and wait for another.
+Parameter $\gamma$ relates to the level of uncertainty surrounding the conditionality of the loan in period two, where smaller values of $\gamma$ denote greater ambiguity.
+This allows the model to capture variation in the ``officialness'' of aid, or the heterogeneity between donors who are more restricted and transparent in the sort of conditions they can impose versus those who have more freedom to set conditions and the clarity surrounding them.
+
+The outcome of the game is that the first donor offers a marginally better loan to the recipient than the second donor $ceteris\;paribus$ (see appendix).
+In other words, in almost all cases the presence of a second credible donor induces competition that benefits the recipient, regardless of the exact nature of donor two's lending practices.
+Unless the recipient is in perfectly extreme need (i.e., $\delta=0$) or the second donor is perfectly shady about it's loans (i.e., $\gamma=0$), then a diversified set of donors induces loans that are more favorable to the recipient.
+
+The first donor's offer is largest, though, when the severity of recipient need is low (high $\delta$) and the second donor is anticipated to implement clear conditions (high $\gamma$).
+This implies the comparative statics that as severity of need increases (i.e., $\delta$ gets smaller) or clarity of conditionality decreases (i.e., $\gamma$ gets smaller), loan value decreases for the recipient.
+Theoretically, loan value to the recipient can be manipulated by either altering the amount of money loaned or by changing the conditions to be imposed.
+
+The above analysis produces the following hypotheses, conditional on the presence of a diverse set of donors:
+
+\begin{align*}
+    H_{1_a}&:\;\text{An increase (decrease) in severity of recipient need will decrease (increase) the amount of money}\\
+    &\;\text{offered via loans}\\
+    H_{1_b}&:\;\text{An increase (decrease) in severity of recipient need will increase (decrease) the stringency of loan}\\
+    &\;\text{conditions}\\
+    H_{2_a}&:\;\text{An increase (decrease) in the clarity of loan conditionality will increase (decrease) the amount of}\\
+    &\;\text{money offered via loans}\\
+    H_{2_b}&:\;\text{An increase (decrease) in the clarity of loan conditionality will decrease (increase) the stringency}\\
+    &\;\text{of loan conditions}\\
+\end{align*}
+
+Implications: the more unofficial, ambiguous loans that a country receives from China, the less competitive offer they will receive from more official, Western flows.
+The more ODA-like, official loans they receive from China, the better offers they will receive from Western institutions.
+
+\section*{Operationalization}
+Western loans (bilateral and multilateral?) as first donor, China as second with the variation in officialness in aid conditionality.
+
 Data \& Variables
+Aiddata for Chinese aid, OECD data for Western aid (World Bank or IMF?), GDP per capita part of need but need a different measure to get at temporal shocks/crises.
 
@@
 \pagebreak
+\section*{Appendix}
+\subsection*{Figure 1}
+\begin{tikzpicture}[scale=1,font=\footnotesize]
+    \tikzstyle{solid node}=[circle,draw,inner sep=1.5,fill=black]
+    \tikzstyle{hollow node}=[circle,draw,inner sep=1.5]
+    \tikzstyle{level 1}=[level distance=2cm,sibling distance=2cm]
+    \tikzstyle{level 2}=[level distance=2cm,sibling distance=2cm]
+    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
+    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
+    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
+    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
+    \node(0)[solid node,label=above:{$D_1$},label=below:{$x_1$}]{}
+        child{node{}}
+        child{node[solid node,label=above:{$R$}]{}
+            child{node[hollow node,label=below:{$1-x_1,\; x_1,\; 0$}]{} edge from parent node[left]{Accept} edge from parent node[right,xshift=10mm]{Reject} edge from parent node[right,xshift=15mm,yshift=30mm]{$0\leq x_{t}<1,\;t=1$}}
+                child{node[solid node,label=above:{$D_2$},label=below:{$x_2$}]{}
+                    child{node{}}
+                        child{node[solid node,label=above:{$R$}]{}
+                                child{node[hollow node,label=below:{$0,\; \delta \gamma x_2,\; 1-\delta \gamma x_2$}]{} edge from parent node[left]{Accept} edge from parent node[right,xshift=10mm]{Reject} edge from parent node[right,xshift=15mm,yshift=35mm]{$0\leq \delta<1,\;0\leq \gamma <1,\;t=2$}}
+                                    child{node[hollow node,label=below:{$0,\;0,\;0$}]{}
+        }
+        }
+        }
+        };
+    \draw[dashed](0-1)to(0-2);
+    \path (-1,-6) node (p1) {};
+    \path (5,-2) node (p2) {};
+    \draw[dashed] (p1) to (p2);
+    \path (1,-6) node (p3) {};
+    \path (3,-6) node (p4) {};
+    \draw[dashed] (p3) to (p4);
+\end{tikzpicture}
+
+The utility functions of the players are simply:
+\begin{align*}
+    U_R&:\;x_t\\
+    U_{D_{t}}&:\;-x_t\;
+\end{align*}
+where $t\in {1,2}$ and $x_t$ is less than one but greater than or equal to zero.
+Making $x_t$ less than one allows for the donors to profit from any loan they make, enabling the offering of loans in the first place.
+
+The parameters $\delta$ and $\gamma$ are all greater than or equal to zero and bounded by one.
+These modeling specifications seem to be without loss of generality, implying that the results are not dependent on these decisions.
+
+Solving the game via backwards induction:
+
+\begin{center}
+\begin{tabular}{c l}
+    $\delta \gamma x_2 >0$ & $R$ accepts $x_2$ iff this inequality is true in period two. \\
+    $x_2= \epsilon$ & $D_2$'s offer, where $\epsilon$ is infinitely small but greater than 0.\\
+    $x_1>\epsilon$ & The condition for $R$ to accept in period one.\\
+    $x_1=2 \epsilon$ & $D_1$'s offer, which $R$ accepts.\\
+\end{tabular}
+\end{center}
+
+Ultimately, $x_1>x_2$.
+Thus, competition alone increases the loan payoff for the recipient.
+These results are augmented by severity of need ($\delta$) and the clarity of conditionality ($\gamma$).
+Smaller values of either of these parameters coincides with smaller loan payoffs to the recipient in period two, which leads to smaller counteroffers by the first donor in period one.
+
+\pagebreak
 \printbibliography

### 2022-11-13 Extra.tex
idea brief

@@
 Is the BRI really an attractive substitute for IMF funding?
+
+----------
+Supply side focus thus far (how donor behavior has been affected).
+Lots of academic attention on supply side provision of aid given China's entrance (e.g., \cite{dreher2018}, \cite{dreher2015}), but few explorations of the demand side after China has become a prevalent donor.
+Also research on how Chinese aid affects recipients in various ways (e.g., \cite{martorano2020}, \cite{bader2015}).
+This paper seeks to address this shortage in the literature, aiming to understand how recipient countries choose between the vast number of credible donors.
+Relevant literature: \cite{kilama2016a}, \cite{hernandez2017}, \cite{li2017a}, \cite{isaksson2018}, \cite{humphrey2019}, \cite{broich2017a}.
 

### 2022-11-13 Paper.tex
idea brief

@@
 \usepackage[utf8]{inputenc}
-\title{\vspace{-2.75cm}634\vspace{-0.5cm}}
+\title{\vspace{-2.75cm}Idea Brief\vspace{-0.5cm}}
 \author{Nicholas Ray}
@@
 \section*{Introduction}
-%Look at Dreher's book, Kidd's international formal theory book, Hernadez 2017 paper, etc.
-BRI (\cite{dreher2022}), Globalization (papers from week 6)?
+The People's Republic of China (China) established the Belt and Road Initiative (BRI) in 2013, a project aimed at increasing both China's global influence and domestic economic growth.
+Since then, China has become the ``lender of first resort'' for developing countries \parencite[1]{dreher2022}.
 
-Lots of academic attention on supply side provision of aid given China's entrance (e.g., \cite{dreher2018}, \cite{dreher2015}), but few explorations of the demand side after China has become a prevalent donor.
-Also research on how Chinese aid affects recipients in various ways (e.g., \cite{martorano2020}, \cite{bader2015}).
-This paper seeks to address this shortage in the literature, aiming to understand how recipient countries choose between the vast number of credible donors.
-Relevant literature: \cite{kilama2016a}, \cite{hernandez2017}, \cite{li2017a}, \cite{isaksson2018}, \cite{humphrey2019}, \cite{broich2017a}.
+There has been an abundance of scholarly work attempting to understand the potential effects of China's recent prominence in the international financing and aid arena.
+Most, if not all, of this literature focuses on how the behavior of other aid donors has been affected (e.g., \cite{humphrey2019}; \cite{kilama2016a}) or how the effectiveness of their aid has changed (e.g., \cite{blair2022}; \cite{gehring2022}).
+Essentially, this work has explored how the supply side of foreign aid has been influenced by China's aid involvement.
 
-Research Question.
-Given the literature, the decision-making of recipient countries no longer seems so trivial (i.e., why are countries choosing to receive aid money from China?).
-The literature implies that there should be a healthy mix of aid donor money given the effects shown, implying that there should be some strategy present in recipient countries.
+However, there has been little research on how Chinese aid affects the demand side of foreign aid (i.e., recipient behavior), despite the supply side literature implying that the presence of Chinese aid is indeed consequential for recipients.
+In particular, it appears that the democratizing effects of aid from the Organization for Economic Cooperation and Development (OECD) has been reduced in light of Chinese aid (\cite{li2017a}) and that the World Bank provides fewer conditions for it's loans to potentially compete with China (\cite{hernandez2017}).
+
+Given this seemingly enhanced foreign aid competition, I argue that recipient behavior is no longer a trivial question, as the conventional wisdom assumes.
+It should be plausible that recipients engage in some strategy to maximize the financial package they receive from donors, possibly diversifying their aid diet to include Chinese funds and gain leverage on Western donors.
+
+To explore the possible strategic behavior of international finance recipients in this situation, I build a formal bargaining model below.
+The model attempts to capture the flexibility of Chinese lending practices and the results of Chinese competition with more traditional, OECD donors.
+
+Empirically, I focus on evaluating the model's implications in Africa using available data on Chinese and Western loans. Data availability for Chinese aid limits the period of interest from 2000-2017.
 
 \section*{Theory}
+\subsection*{Model}
 In an attempt to model the effects of having more than one donor on recipient behavior, especially when donors display heterogeneity in their loaning practices, I formalize a bargaining interaction between a recipient country and two types of donors.
@@
 
+\subsection*{Implications}
 The first donor's offer is largest, though, when the severity of recipient need is low (high $\delta$) and the second donor is anticipated to implement clear conditions (high $\gamma$).
 This implies the comparative statics that as severity of need increases (i.e., $\delta$ gets smaller) or clarity of conditionality decreases (i.e., $\gamma$ gets smaller), loan value decreases for the recipient.
-Theoretically, loan value to the recipient can be manipulated by either altering the amount of money loaned or by changing the conditions to be imposed.
+This analysis produces the following hypotheses, conditional on the presence of a diverse set of donors:
+\begin{align*}
+    &\textbf{Recipient Need is Inversely Related to Loan Value}\\
+    H_{1_a}&:\;\text{An increase in severity of recipient need will decrease the amount of money offered via loans}\\
+    H_{1_b}&:\;\text{A decrease in severity of recipient need will increase the amount of money offered via loans}\\
+    &\textbf{Condition Clarity is Directly Related to Loan Value}\\
+    H_{2_a}&:\;\text{An increase in the clarity of loan conditionality will increase the amount of money offered via loans}\\
+    H_{2_b}&:\;\text{A decrease in the clarity of loan conditionality will decrease the amount of money offered via loans}\\
+\end{align*}
+In other words, I expect to find the following relationship:
 
-The above analysis produces the following hypotheses, conditional on the presence of a diverse set of donors:
+\subsection*{Table 1}
+\begin{tabular}{c|c c }
+    & Severity of Recipient Need & Clarity of Loan Conditionality\\
+    \hline
+    High & Low Loan Value & High Loan Value\\
+    Low & High Loan Value & Low Loan Value\\
+\end{tabular}
 
-\begin{align*}
-    H_{1_a}&:\;\text{An increase (decrease) in severity of recipient need will decrease (increase) the amount of money}\\
-    &\;\text{offered via loans}\\
-    H_{1_b}&:\;\text{An increase (decrease) in severity of recipient need will increase (decrease) the stringency of loan}\\
-    &\;\text{conditions}\\
-    H_{2_a}&:\;\text{An increase (decrease) in the clarity of loan conditionality will increase (decrease) the amount of}\\
-    &\;\text{money offered via loans}\\
-    H_{2_b}&:\;\text{An increase (decrease) in the clarity of loan conditionality will decrease (increase) the stringency}\\
-    &\;\text{of loan conditions}\\
-\end{align*}
+\section*{Empirics}
+\subsection*{Operationalization}
+To evaluate the theoretical expectations I focus on the international loan environment in Africa since the year 2000.
+Loan value, or the total sum of money being loaned to an African country, is the dependent variable.
+The main explanatory variables of interest are recipient need and the clarity of loan conditionality.
+Recipient need is captured by gross domestic product (GDP) per capita while the clarity of loan conditionality will be an indicator for how ``offical'' aid is.
+Thus, the empirical model is:
 
-Implications: the more unofficial, ambiguous loans that a country receives from China, the less competitive offer they will receive from more official, Western flows.
-The more ODA-like, official loans they receive from China, the better offers they will receive from Western institutions.
+$\text{Loan Value}= \beta_0 + \beta_1 \text{GDP per capita}+ \beta_2 \text{Loan Conditionality}+ \gamma_i x_i + \varepsilon$,
 
-\section*{Operationalization}
-Western loans (bilateral and multilateral?) as first donor, China as second with the variation in officialness in aid conditionality.
+where $x_i$ is a vector of controls.
 
-Data \& Variables
-Aiddata for Chinese aid, OECD data for Western aid (World Bank or IMF?), GDP per capita part of need but need a different measure to get at temporal shocks/crises.
+\subsection*{Data \& Variables}
+For data on international loans, I use data from William \& Mary's ``Aiddata'' lab for Chinese loans (\cite{custer2021}) and data from the OECD on Western loans (\cite{oecd2022}).
+GDP per capita stems from the World Bank (\cite{bank2022}) while I am currently exploring measures for loan conditionality.
+The most overly-simplistic (and not accurate) idea is to label all Chinese loans as ``low'' or ``vague'' in their conditionality while rating all Western loans as ``high'' or ``clear'' in their loan conditions.
+There is data on World Bank conditionality, though, (see \cite{hernandez2017}, for example) but I have yet to analyze the Chinese data for conditionality measures.
 
-Research Design
+\subsection*{Estimation}
+I plan to estimate the regression equation above using panel data and OLS with country-fixed effects and clustered standard errors by country.
 

### 2022-12-08 Other/Future.tex
Updates from Overleaf

Weak logical link between Western entities giving fewer concessions and the conclusion that recipients should diversify borrowing

We're implicitly assuming that loans are sufficiently easy for African countries to obtain from both China and West. Big problem

### 2022-12-08 Paper.tex
Updates from Overleaf

--- 2022-10-04 Paper.tex
@@
 \usepackage[utf8]{inputenc}
-\title{\vspace{-2.75cm}634\vspace{-0.5cm}}
+\title{\vspace{-2.75cm}On Government Borrowing Behavior\vspace{-0.5cm}}
 \author{Nicholas Ray}
-\date{\vspace{-0.30cm}October 31 2022\vspace{-1cm}}
+\date{\vspace{-0.30cm}December 7 2022\vspace{-1cm}}
 \usepackage[margin=1in]{geometry}
@@
 \section*{Introduction}
-%Look at Dreher's book, Kidd's international formal theory book, Hernadez 2017 paper, etc.
-BRI (\cite{dreher2022}), Globalization (papers from week 6)?
+Since engaging in a ``going out'' strategy around the turn of the century, the People's Republic of China (China) has successfully become the ``lender of first resort'' for developing countries \parencite[1]{dreher2022}.
+There has been an abundance of scholarly work attempting to understand the potential effects of China's contemporary prominence in the global finance arena.
+Much of this literature focuses on how the international financing behavior of more traditional, Western donors have been affected (e.g., \cite{humphrey2019}; \cite{kilama2016a}) or how the effectiveness of their money has changed (e.g., \cite{blair2022}; \cite{gehring2022}).
 
-Lots of academic attention on supply side provision of aid given China's entrance (e.g., \cite{dreher2018}, \cite{dreher2015}), but few explorations of the demand side after China has become a prevalent donor.
-Also research on how Chinese aid affects recipients in various ways (e.g., \cite{martorano2020}, \cite{bader2015}).
-This paper seeks to address this shortage in the literature, aiming to understand how recipient countries choose between the vast number of credible donors.
-Relevant literature: \cite{kilama2016a}, \cite{hernandez2017}, \cite{li2017a}, \cite{isaksson2018}, \cite{humphrey2019}, \cite{broich2017a}.
+Little of this work has looked at how the behavior of recipients of international finance has updated since the availability of Chinese money.
+This lack of attention is despite recent work that implies that recipient countries may extract benefits from their loan choices in a more Chinese global finance environment.
+While the literature implies that recipients stand to gain from receiving both Chinese and Western finance and the subsequently more competitive terms, observations of borrowing practices in Africa do not seemingly reflect that countries take relatively similar levels of both loan types.
 
-Research Question.
-Given the literature, the decision-making of recipient countries no longer seems so trivial (i.e., why are countries choosing to receive aid money from China?).
-The literature implies that there should be a healthy mix of aid donor money given the effects shown.
-Some strategy is no involved on behalf of the recipient country; if we are not seeing a diversified diet in aid receipt, why not?
-Seems best.
+I argue that this is due to time-inconsistency problems where countries prefer Western or Chinese loans over the other in the short-run.
+Understanding the debt composition of developing countries is an increasingly important issue as public debt continues to rise.
+This research could also shed light on literature concerned about China's interaction with the liberal international order (LIO) and spark a new research agenda studying recipient behavior.
 
-\section*{Theory}
-Explanation
+\section*{What Demands Explanation and Why}
+There is evidence that countries are offered fewer loan conditions from the World Bank (\cite{hernandez2017}) and that Western aid is less sensitive to policy and institutional quality (\cite{annen2021}) when they are recipients of Chinese finance.
+Although Dreher et al.
+(2021)\nocite{dreher2021} did not find a sizable negative effect of Chinese finance on Western aid's effectiveness, they did find that aid from the United States (U.S.) seems to be more effective in the absence of Chinese finance.
+In sum, this evidence suggests that receiving Chinese loans may induce the additional benefit of better financial terms from subsequent Western lenders.
 
-\section*{Methodology}
-Data \& Variables
+There is also evidence that Chinese finance increases with Western development assistance, which Dreher et al.
+(2018)\nocite{dreher2018} interpret as competitive behavior from China.
+Taken together, the literature seems to imply that there is some financial competition between the West and China that recipients may be able to take advantage of to procure more favorable borrowing terms.
+It follows that recipients should have a relatively diversified composition of debt between Chinese and Western lenders to stimulate this competition and term improvement.
 
-Research Design
+However, it is at least observed in Africa that the proportion of Chinese loans to Western loans varies substantially between counties and further that some countries almost entirely borrow from either China or the West when taking money from governments.
+For example, compare table 1 and table 2, which show the estimated composition of public debt in Cabo Verde and Djibouti, respectively (\cite{jubileedebtcampaign2018}).
+Cabo Verde owes only 1\% of its estimated total debt to China while debt to Portugal and other unspecified countries exceeds 25\%.
+In Djibouti, meanwhile, 68\% of its estimated debt can be attributed to China.
 
+\begin{table}
+    \centering
+    \includegraphics[scale=0.5]{Figures/CaboVerde.png}
+    \caption{Estimated Debt for Cabo Verde}
+    \vspace{1cm}
+    \includegraphics[scale=0.5025]{Figures/Djibouti.png}
+    \caption{Estimated Debt for Djibouti}
+\end{table}
+
+Thus, the variance in debt composition and the seeming failure of countries to borrow in a more equal manner between China and Western entities must be explained.
+In other words, how do recipient countries decide between taking loans from China and the West?
+Taking loans is costly, at least in the long-run, and recipients presumably want to maximize the payoff they receive from borrowing.
+Related literature seems to not have fully considered recipient decision-making with regard to choosing a borrower, instead largely focusing on macroeconomic and political determinants of government debt (e.g., \cite{bittencourt2015} ; \cite{swamy2015}) or the determinants of lender behavior (e.g., \cite{dreher2018}).
+
+\section*{My Explanation}
+I argue that the variation observed in African borrowing practices is a result of strategic considerations on behalf of recipients.
+Specifically, I argue that some countries take Chinese and Western finance at substantially different rates due to dissimilarities in the conditions of Western and Chinese loans and the subsequent evaluations of loan value by recipients.
+
+There is evidence that China might be simultaneously more strict on the economic conditions on their finance (e.g., \cite{dreher2018}) while also less strict on the political conditions imposed (e.g., \cite{dreher2018}).
+Western loans, by contrast, seem more politically strict than economic (\cite{hernandez2017}).
+This dissimilarity leads to time-inconsistency problems, where in the short-term countries prefer either less severe economic or political conditions instead of minimizing the joint conditionality over the long-term.
+
+One implication is that more democratic countries should be more sensitive to explicitly political conditions and, thus, prefer Western loans $ceteris\;paribus$.
+This could also explain Dreher et al.'s (2018) findings that Chinese loans seem to flow to more corrupt countries and those with poorer political institutions.
+
+\subsubsection*{Figure 1: Non-Democratic Country Loan Preference, $ceteris\;paribus$}
+\begin{tikzpicture}[scale=2,declare function={F(\x) = 1.7*(2*\x-\x*\x)-0.2;}]
+  \draw[-latex] (0,-0.2) -- (0,2) node[left]{$Utility$};
+  \draw[-latex] (-0.2,0) -- (2,0) node[below right]{$Political\;Conditionality$};
+  \draw[domain=0.1:1.9,samples=10,smooth,thick] plot (\x, {F(\x)}); 
+  \coordinate (max) at (0,{F(1)});
+  \draw[dashed] (max) -| (1,0) node[pos=1,below]{China};
+  \coordinate (max) at (0,{F(1.5)});
+  \draw[dashed] (max) -| (1.5,0) node[pos=1,below]{West};
+\end{tikzpicture}
+
+\section*{Research Design}
+The implication above leads to the following hypotheses:
+\begin{align*}
+    H_{1a}&:\;\text{Democracies should receive more Western loans than Chinese loans}\\
+    H_{1b}&:\;\text{Non-democracies should receive more Chinese loans than Western loans}\\
+\end{align*}
+To test these hypotheses I intend to focus on the international loan environment in Africa since from the years 2000 to 2020 due the continent being a major area of focus for China's finance projects and this being the time period most relevant for Chinese finance.
+I will fit a logit/probit model with the lender type (e.g., majority Western or not) as my dependent variable.
+The main explanatory variables will be regime type and a measure for loan conditionality.
+Ideally, an instrumental variable will be used for regime type since there is theoretically expected to be simultaneity present.
+Further, I will include gross domestic product (GDP) per capita as a control for recipient need and an additional control for the gross sum of the loan to ensure comparison.
+
+I plan to use data from William \& Mary's ``Aiddata'' lab for Chinese loans (\cite{custer2021}) and data from the Organization for Economic Co-operation and Development (OECD) on Western loans (\cite{organizationforeconomicco-operationanddevelopment2022a}).
+GDP per capita stems from the United Nations (\cite{unitednationsstatisticsdivision2019}).
+For regime type, I intend to use an updated version of Cheibub et al.'s dictatorship and democracy index (\cite{cheibub2010}).
+
+\nocite{curini2020}
 \pagebreak

### 2022-12-08 Other/ExtraMaterial.tex

--- 2022-11-13 Extra.tex
@@
-\section*{What needs to be explained}
+\section*{Rough Draft}
+
+\section*{Idea Brief}
+\subsection*{What needs to be explained}
 Given the seeming consensus of economic and political deglobalization,  namely in the West, there is attention being paid to China's position in this story, whether as a cause or of an effect.
@@
 Supply side focus thus far (how donor behavior has been affected).
-Lots of academic attention on supply side provision of aid given China's entrance (e.g., \cite{dreher2018}, \cite{dreher2015}), but few explorations of the demand side after China has become a prevalent donor.
+Lots of academic attention on supply side provision of aid given China's entrance (e.g., \scite{dreher2018}, \cite{dreher2015}), but few explorations of the demand side after China has become a prevalent donor.
 Also research on how Chinese aid affects recipients in various ways (e.g., \cite{martorano2020}, \cite{bader2015}).
@@
 
-\section*{Theory} 
+\subsection*{Theory} 
 Given that there are more than one donors offering money, recipients pick the sum that maximizes their utility.
@@
 
-\section*{Alternative Explanations}
+\subsection*{Alternative Explanations}
 
-\section*{Methodology}
+\subsection*{Methodology}
 Some descriptive stats on foreign aid spending by country and organization over time.
@@
 
-\section*{Complications}
+\subsection*{Complications}

### 2022-12-08 PreviousVersions/IdeaBrief.tex

\section*{Introduction}
The People's Republic of China (China) established the Belt and Road Initiative (BRI) in 2013, a project aimed at increasing both China's global influence and domestic economic growth. Since then, China has become the ``lender of first resort'' for developing countries \parencite[1]{dreher2022}.

There has been an abundance of scholarly work attempting to understand the potential effects of China's recent prominence in the international financing and aid arena. Most, if not all, of this literature focuses on how the behavior of other aid donors has been affected (e.g., \cite{humphrey2019}; \cite{kilama2016a}) or how the effectiveness of their aid has changed (e.g., \cite{blair2022}; \cite{gehring2022}). Essentially, this work has explored how the supply side of foreign aid has been influenced by China's aid involvement.

However, there has been little research on how Chinese aid affects the demand side of foreign aid (i.e., recipient behavior), despite the supply side literature implying that the presence of Chinese aid is indeed consequential for recipients. In particular, it appears that the democratizing effects of aid from the Organization for Economic Cooperation and Development (OECD) has been reduced in light of Chinese aid (\cite{li2017a}) and that the World Bank provides fewer conditions for it's loans to potentially compete with China (\cite{hernandez2017}).

Given this seemingly enhanced foreign aid competition, I argue that recipient behavior is no longer a trivial question, as the conventional wisdom assumes. It should be plausible that recipients engage in some strategy to maximize the financial package they receive from donors, possibly diversifying their aid diet to include Chinese funds and gain leverage on Western donors.

To explore the possible strategic behavior of international finance recipients in this situation, I build a formal bargaining model below. The model attempts to capture the flexibility of Chinese lending practices and the results of Chinese competition with more traditional, OECD donors.

Empirically, I focus on evaluating the model's implications in Africa using available data on Chinese and Western loans. Data availability for Chinese aid limits the period of interest from 2000-2017.

\section*{Theory}
\subsection*{Model}
In an attempt to model the effects of having more than one donor on recipient behavior, especially when donors display heterogeneity in their loaning practices, I formalize a bargaining interaction between a recipient country and two types of donors. Figure 1 illustrates the extensive-form of the interaction and can be found in the appendix.

Bargaining occurs over two periods, with the first donor ($D_1$) making an initial loan offer ($x_1$) to the recipient ($R$). If the recipient accepts the loan, the first donor gets a payoff ($1-x_1$) that corresponds to the expected benefits from the conditions of the loan (e.g., political reform, trade liberalization). The recipient gains the value of the loan, $x_1$.

If the recipient rejects the offer, then the second donor ($D_2$) has an opportunity to proffer a loan ($x_2$). Acceptance by the recipient in this second period yields similar payoffs to those in the first (i.e., $1-x_2$ and $x_2$), except now there are two additional parameters, $\delta$ and $\gamma$, such that the recipient's value of the loan in the second period totals to $\delta \gamma x_2$. Consequently, the donor would receive $1-\delta \gamma x_2$ if the offer is accepted.

The parameter $\delta$ commonly appears in multi-period bargaining models and is referred to as a discount factor. The substantive interpretation in this scenario is that recipients shopping for loans have some time sensitive reason for wanting a loan, such as an economic crisis. The smaller that $\delta$ is, the more harmful it is for recipients to refuse the first loan offer they receive and wait for another. Parameter $\gamma$ relates to the level of uncertainty surrounding the conditionality of the loan in period two, where smaller values of $\gamma$ denote greater ambiguity. This allows the model to capture variation in the ``officialness'' of aid, or the heterogeneity between donors who are more restricted and transparent in the sort of conditions they can impose versus those who have more freedom to set conditions and the clarity surrounding them.

The outcome of the game is that the first donor offers a marginally better loan to the recipient than the second donor $ceteris\;paribus$ (see appendix). In other words, in almost all cases the presence of a second credible donor induces competition that benefits the recipient, regardless of the exact nature of donor two's lending practices. Unless the recipient is in perfectly extreme need (i.e., $\delta=0$) or the second donor is perfectly shady about it's loans (i.e., $\gamma=0$), then a diversified set of donors induces loans that are more favorable to the recipient.

\subsection*{Implications}
The first donor's offer is largest, though, when the severity of recipient need is low (high $\delta$) and the second donor is anticipated to implement clear conditions (high $\gamma$). This implies the comparative statics that as severity of need increases (i.e., $\delta$ gets smaller) or clarity of conditionality decreases (i.e., $\gamma$ gets smaller), loan value decreases for the recipient. This analysis produces the following hypotheses, conditional on the presence of a diverse set of donors:
\begin{align*}
    &\textbf{Recipient Need is Inversely Related to Loan Value}\\
    H_{1_a}&:\;\text{An increase in severity of recipient need will decrease the amount of money offered via loans}\\
    H_{1_b}&:\;\text{A decrease in severity of recipient need will increase the amount of money offered via loans}\\
    &\textbf{Condition Clarity is Directly Related to Loan Value}\\
    H_{2_a}&:\;\text{An increase in the clarity of loan conditionality will increase the amount of money offered via loans}\\
    H_{2_b}&:\;\text{A decrease in the clarity of loan conditionality will decrease the amount of money offered via loans}\\
\end{align*}
In other words, I expect to find the following relationship:

\subsection*{Table 1}
\begin{tabular}{c|c c }
    & Severity of Recipient Need & Clarity of Loan Conditionality\\
    \hline
    High & Low Loan Value & High Loan Value\\
    Low & High Loan Value & Low Loan Value\\
\end{tabular}

\section*{Empirics}
\subsection*{Operationalization}
To evaluate the theoretical expectations I focus on the international loan environment in Africa since the year 2000. Loan value, or the total sum of money being loaned to an African country, is the dependent variable. The main explanatory variables of interest are recipient need and the clarity of loan conditionality. Recipient need is captured by gross domestic product (GDP) per capita while the clarity of loan conditionality will be an indicator for how ``offical'' aid is. Thus, the empirical model is:

$\text{Loan Value}= \beta_0 + \beta_1 \text{GDP per capita}+ \beta_2 \text{Loan Conditionality}+ \gamma_i x_i + \varepsilon$,

where $x_i$ is a vector of controls.

\subsection*{Data \& Variables}
For data on international loans, I use data from William \& Mary's ``Aiddata'' lab for Chinese loans (\cite{custer2021}) and data from the OECD on Western loans (\cite{oecd2022}). GDP per capita stems from the World Bank (\cite{bank2022}) while I am currently exploring measures for loan conditionality. The most overly-simplistic (and not accurate) idea is to label all Chinese loans as ``low'' or ``vague'' in their conditionality while rating all Western loans as ``high'' or ``clear'' in their loan conditions. There is data on World Bank conditionality, though, (see \cite{hernandez2017}, for example) but I have yet to analyze the Chinese data for conditionality measures.

\subsection*{Estimation}
I plan to estimate the regression equation above using panel data and OLS with country-fixed effects and clustered standard errors by country.

\pagebreak
\section*{Appendix}
\subsection*{Figure 1}
\begin{tikzpicture}[scale=1,font=\footnotesize]
    \tikzstyle{solid node}=[circle,draw,inner sep=1.5,fill=black]
    \tikzstyle{hollow node}=[circle,draw,inner sep=1.5]
    \tikzstyle{level 1}=[level distance=2cm,sibling distance=2cm]
    \tikzstyle{level 2}=[level distance=2cm,sibling distance=2cm]
    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
    \tikzstyle{level 3}=[level distance=2cm,sibling distance=2cm]
    \node(0)[solid node,label=above:{$D_1$},label=below:{$x_1$}]{}
        child{node{}}
        child{node[solid node,label=above:{$R$}]{}
            child{node[hollow node,label=below:{$1-x_1,\; x_1,\; 0$}]{} edge from parent node[left]{Accept} edge from parent node[right,xshift=10mm]{Reject} edge from parent node[right,xshift=15mm,yshift=30mm]{$0\leq x_{t}<1,\;t=1$}}
                child{node[solid node,label=above:{$D_2$},label=below:{$x_2$}]{}
                    child{node{}}
                        child{node[solid node,label=above:{$R$}]{}
                                child{node[hollow node,label=below:{$0,\; \delta \gamma x_2,\; 1-\delta \gamma x_2$}]{} edge from parent node[left]{Accept} edge from parent node[right,xshift=10mm]{Reject} edge from parent node[right,xshift=15mm,yshift=35mm]{$0\leq \delta<1,\;0\leq \gamma <1,\;t=2$}}
                                    child{node[hollow node,label=below:{$0,\;0,\;0$}]{}
        }
        }
        }
        };
    \draw[dashed](0-1)to(0-2);
    \path (-1,-6) node (p1) {};
    \path (5,-2) node (p2) {};
    \draw[dashed] (p1) to (p2);
    \path (1,-6) node (p3) {};
    \path (3,-6) node (p4) {};
    \draw[dashed] (p3) to (p4);
\end{tikzpicture}

The utility functions of the players are simply:
\begin{align*}
    U_R&:\;x_t\\
    U_{D_{t}}&:\;-x_t\;
\end{align*}
where $t\in {1,2}$ and $x_t$ is less than one but greater than or equal to zero. Making $x_t$ less than one allows for the donors to profit from any loan they make, enabling the offering of loans in the first place.

The parameters $\delta$ and $\gamma$ are all greater than or equal to zero and bounded by one. These modeling specifications seem to be without loss of generality, implying that the results are not dependent on these decisions.

Solving the game via backwards induction:

\begin{center}
\begin{tabular}{c l}
    $\delta \gamma x_2 >0$ & $R$ accepts $x_2$ iff this inequality is true in period two. \\
    $x_2= \epsilon$ & $D_2$'s offer, where $\epsilon$ is infinitely small but greater than 0.\\
    $x_1>\epsilon$ & The condition for $R$ to accept in period one.\\
    $x_1=2 \epsilon$ & $D_1$'s offer, which $R$ accepts.\\
\end{tabular}
\end{center}

Ultimately, $x_1>x_2$. Thus, competition alone increases the loan payoff for the recipient. These results are augmented by severity of need ($\delta$) and the clarity of conditionality ($\gamma$). Smaller values of either of these parameters coincides with smaller loan payoffs to the recipient in period two, which leads to smaller counteroffers by the first donor in period one.

### 2022-12-13 Other/Future.tex
hyperref

@@
 We're implicitly assuming that loans are sufficiently easy for African countries to obtain from both China and West. Big problem
+%%%%%%%%%%%%%%%%%%
+need to hit hard the "suggestion" from the literature. what exactly is suggested and how do you synthesize that into expectations that seem unobserved thus far?
+
+Really hit the time inconsistency argument. what should countries gain in the long run? why do temporally close considerations disrupt their ability to obtain this?
+
+How does your explanation interact with alternatives?
+Aren't there some major differences between Cabo Verde and Djibouti, for example?
+What else might explain why China is a large lender in the later but not the former, relatively speaking?

### 2022-12-13 Paper.tex
hyperref

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \doublespacing
+\usepackage[colorlinks,citecolor=cyan,urlcolor=blue,bookmarks=false,hypertexnames=true]{hyperref}
 \usepackage[backend=biber, style=authoryear, maxbibnames=99, uniquelist=false]{biblatex}
@@
 }
-\addbibresource{ForeignAidBib.bib}
+\DeclareCiteCommand{\citeyear}
+    {\usebibmacro{prenote}}
+    {\bibhyperref{\printfield{year}}\bibhyperref{\printfield{extrayear}}}
+    {\multicitedelim}
+    {\usebibmacro{postnote}}
+
+\DeclareCiteCommand{\citeyearpar}[\mkbibparens]
+    {\usebibmacro{prenote}}
+    {\bibhyperref{\printfield{year}}\bibhyperref{\printfield{extrayear}}}
+    {\multicitedelim}
+    {\usebibmacro{postnote}}
+\addbibresource{ForeignAid.bib}
 \begin{document}
 \maketitle
+\begin{abstract}
+
+\end{abstract}
+
+\textit{Keywords}:
+
 \section*{Introduction}
@@
 
-Little of this work has looked at how the behavior of recipients of international finance has updated since the availability of Chinese money.
+Little of this work, however, has looked at how the behavior of recipients of international finance has updated since the availability of Chinese money.
 This lack of attention is despite recent work that implies that recipient countries may extract benefits from their loan choices in a more Chinese global finance environment.
-While the literature implies that recipients stand to gain from receiving both Chinese and Western finance and the subsequently more competitive terms, observations of borrowing practices in Africa do not seemingly reflect that countries take relatively similar levels of both loan types.
+While the literature suggests that recipients stand to gain from receiving both Chinese and Western finance and the subsequently more competitive terms, observations of borrowing practices in Africa do not seemingly reflect that recipients are engaging in a strategy to leverage competition between lenders.
+% i.e., that countries take relatively similar levels of both loan types.
 
@@
 Although Dreher et al.
-(2021)\nocite{dreher2021} did not find a sizable negative effect of Chinese finance on Western aid's effectiveness, they did find that aid from the United States (U.S.) seems to be more effective in the absence of Chinese finance.
+\citeyear{dreher2021} did not find a sizable negative effect of Chinese finance on Western aid's effectiveness, they did find that aid from the United States (U.S.) seems to be more effective in the absence of Chinese finance.
 In sum, this evidence suggests that receiving Chinese loans may induce the additional benefit of better financial terms from subsequent Western lenders.
@@
 There is also evidence that Chinese finance increases with Western development assistance, which Dreher et al.
-(2018)\nocite{dreher2018} interpret as competitive behavior from China.
+\citeyear{dreher2018} interpret as competitive behavior from China.
 Taken together, the literature seems to imply that there is some financial competition between the West and China that recipients may be able to take advantage of to procure more favorable borrowing terms.

### 2022-12-15 Paper.tex
updates

@@
     {\usebibmacro{postnote}}
-
 \DeclareCiteCommand{\citeyearpar}[\mkbibparens]
@@
 \section*{Introduction}
-Since engaging in a ``going out'' strategy around the turn of the century, the People's Republic of China (China) has successfully become the ``lender of first resort'' for developing countries \parencite[1]{dreher2022}.
-There has been an abundance of scholarly work attempting to understand the potential effects of China's contemporary prominence in the global finance arena.
+Since engaging in a ``going out'' strategy around the turn of the century, the People's Republic of China (China) has successfully become the ``lender of first resort'' for developing countries \parencite[1]{dreher2022}.\footnote{All R code, data, and \LaTeX \;code underlying my analysis can be found in the corresponding repository on GitHub at https://github.com/nnray.} There has been an abundance of scholarly work attempting to understand the potential effects of China's contemporary prominence in the global finance arena.
 Much of this literature focuses on how the international financing behavior of more traditional, Western donors have been affected (e.g., \cite{humphrey2019}; \cite{kilama2016a}) or how the effectiveness of their money has changed (e.g., \cite{blair2022}; \cite{gehring2022}).
@@
 This research could also shed light on literature concerned about China's interaction with the liberal international order (LIO) and spark a new research agenda studying recipient behavior.
+\textbf{more about contributions}
+
+\textbf{layout of the paper}
 
 \section*{What Demands Explanation and Why}
-There is evidence that countries are offered fewer loan conditions from the World Bank (\cite{hernandez2017}) and that Western aid is less sensitive to policy and institutional quality (\cite{annen2021}) when they are recipients of Chinese finance.
+There is evidence that African countries are offered fewer loan conditions from the World Bank (\cite{hernandez2017}) and that Western aid is less sensitive to policy and institutional quality (\cite{annen2021}) when they are recipients of Chinese finance.
 Although Dreher et al.
-\citeyear{dreher2021} did not find a sizable negative effect of Chinese finance on Western aid's effectiveness, they did find that aid from the United States (U.S.) seems to be more effective in the absence of Chinese finance.
-In sum, this evidence suggests that receiving Chinese loans may induce the additional benefit of better financial terms from subsequent Western lenders.
+\citeyear{dreher2021} did not find that the effectiveness of aid from the United States (U.S.) is negatively affected by the presence of Chinese aid, their results do suggest that U.S.
+aid effectiveness increases in the absence of Chinese aid.
+In sum, this evidence intimates that Western entities are changing their international financial behavior in response to China in a way that benefits recipients.
 
-There is also evidence that Chinese finance increases with Western development assistance, which Dreher et al.
-\citeyear{dreher2018} interpret as competitive behavior from China.
+There is also tentative evidence that China reciprocates these actions.
+Dreher et al.
+\citeyear{dreher2018} find that Chinese finance increases with Western development assistance, which they interpret as competitive behavior from China.
 Taken together, the literature seems to imply that there is some financial competition between the West and China that recipients may be able to take advantage of to procure more favorable borrowing terms.
-It follows that recipients should have a relatively diversified composition of debt between Chinese and Western lenders to stimulate this competition and term improvement.
+If recipients value better loan terms, including lower conditionality, and are willing to take on more debt, it follows that they should be attempting to stimulate this competition by diversifying their loan diet to include both Western and Chinese debt.
+While this logic stemming from the literature does not stipulate an exact proportion of Western finance to Chinese finance that optimizes recipient benefits, it should not be the case that countries borrow exclusively from one or the other.
+Interrogatively, do African countries at the center of this seeming financial competition borrow from the West and China at similar rates to benefit from their competition?
 
-However, it is at least observed in Africa that the proportion of Chinese loans to Western loans varies substantially between counties and further that some countries almost entirely borrow from either China or the West when taking money from governments.
+A cursory view of African debt suggests that this is not universally the case.
+The proportion of Chinese loans to Western loans varies substantially between counties and further that some countries almost entirely borrow from either China or the West when taking money from governments.
 For example, compare table 1 and table 2, which show the estimated composition of public debt in Cabo Verde and Djibouti, respectively (\cite{jubileedebtcampaign2018}).
@@
 
+\begin{table}
+    \centering
+    \includegraphics[scale=0.53]{Figures/summary1.png}
+    \caption{Summary Table of Debt and Loans in Africa}
+\end{table}
+
 \section*{My Explanation}
@@
 
+%going back to the motivating example of Cabo Verde and Djibouti, these examples indeed fit this story as Cabo Verde is much more ``free'' than Djibouti, at least according to Freedom House
+
 One implication is that more democratic countries should be more sensitive to explicitly political conditions and, thus, prefer Western loans $ceteris\;paribus$.
-This could also explain Dreher et al.'s (2018) findings that Chinese loans seem to flow to more corrupt countries and those with poorer political institutions.
+This could also explain Dreher et al.'s (\citeyear{dreher2018}) findings that Chinese loans seem to flow to more corrupt countries and those with poorer political institutions.
 
@@
 
+\section*{Preliminary Analysis}
+
+\begin{table}
+    \centering
+    \includegraphics[scale=0.53]{Figures/summary2.png}
+    \caption{Summary Table of Variables}
+\end{table}
+
+\begin{table}
+    \centering
+    \includegraphics[scale=0.53]{Figures/summary3.png}
+    \caption{Summary Table of Variables}
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{Accounting for Variation in the Ratio between Chinese and World Bank Loans} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-2} 
+\\[-1.8ex] & Ratio (China/World Bank) \\ 
+\hline \\[-1.8ex] 
+ GDP per capita & $-$0.030$^{***}$ \\ 
+  & (0.007) \\ 
+  & \\ 
+ Polity & $-$1.379 \\ 
+  & (4.243) \\ 
+  & \\ 
+\hline \\[-1.8ex] 
+Observations & 874 \\ 
+R$^{2}$ & 0.024 \\ 
+Adjusted R$^{2}$ & $-$0.059 \\ 
+F Statistic & 9.792$^{***}$ (df = 2; 805) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+\section*{Discussion and Conclusion}
+
 \nocite{curini2020}

### 2022-12-15 Other/ExtraMaterial.tex
Final Proposal

@@
 \section*{Rough Draft}
+This dissimilarity leads to time-inconsistency problems, where in the short-term countries prefer either less severe economic or political conditions instead of minimizing the joint conditionality over the long-term.
+
+One implication is that more democratic countries should be more sensitive to explicitly political conditions and, thus, prefer Western loans $ceteris\;paribus$.
+
+\subsubsection*{Figure 1: Non-Democratic Country Loan Preference, $ceteris\;paribus$}
+\begin{tikzpicture}[scale=2,declare function={F(\x) = 1.7*(2*\x-\x*\x)-0.2;}]
+  \draw[-latex] (0,-0.2) -- (0,2) node[left]{$Utility$};
+  \draw[-latex] (-0.2,0) -- (2,0) node[below right]{$Political\;Conditionality$};
+  \draw[domain=0.1:1.9,samples=10,smooth,thick] plot (\x, {F(\x)}); 
+  \coordinate (max) at (0,{F(1)});
+  \draw[dashed] (max) -| (1,0) node[pos=1,below]{China};
+  \coordinate (max) at (0,{F(1.5)});
+  \draw[dashed] (max) -| (1.5,0) node[pos=1,below]{West};
+\end{tikzpicture}
 

### 2022-12-15 Paper.tex
Final Proposal

@@
 \author{Nicholas Ray}
-\date{\vspace{-0.30cm}December 7 2022\vspace{-1cm}}
+\date{\vspace{-0.30cm}December 15 2022\vspace{-1cm}}
 \usepackage[margin=1in]{geometry}
@@
 \begin{abstract}
-
+    In this proposal, I argue that the observed variation in borrowing behavior by recipient countries in Africa can be explained by the dissonant conditionalities associated with Chinese and Western loans.
+Autocracies, who find it more costly to accept Western loans due to the West's historical emphasis on liberal political reforms, accept Western loans at an inefficiently low rate and forgo potentially lower conditions stemming from Chinese loan competition.
+I test the hypothesis that African autocracies have higher proportions of Chinese loans to World Bank loans but do not find support for the statistical importance of regime type.
+GDP per capita, though, seems to be inversely related with the ratio of Chinese loans to World Bank loans.
 \end{abstract}
-
-\textit{Keywords}:
+\vspace{0.5cm}
+\textit{Keywords}: Global Finance, China, World Bank, Africa, Regime Type
 
@@
 While the literature suggests that recipients stand to gain from receiving both Chinese and Western finance and the subsequently more competitive terms, observations of borrowing practices in Africa do not seemingly reflect that recipients are engaging in a strategy to leverage competition between lenders.
-% i.e., that countries take relatively similar levels of both loan types.
 
-I argue that this is due to time-inconsistency problems where countries prefer Western or Chinese loans over the other in the short-run.
 Understanding the debt composition of developing countries is an increasingly important issue as public debt continues to rise.
 This research could also shed light on literature concerned about China's interaction with the liberal international order (LIO) and spark a new research agenda studying recipient behavior.
-\textbf{more about contributions}
 
-\textbf{layout of the paper}
+In the next section I detail what observation is currently not explained and why it should be.
+My explanation and hypothesis follows.
+I then introduce my research design and present preliminary results before moving to a discussion of limitations and contributions of the paper.
 
@@
 Although Dreher et al.
-\citeyear{dreher2021} did not find that the effectiveness of aid from the United States (U.S.) is negatively affected by the presence of Chinese aid, their results do suggest that U.S.
+(\citeyear{dreher2021}) did not find that the effectiveness of aid from the United States (U.S.) is negatively affected by the presence of Chinese aid, their results do suggest that U.S.
 aid effectiveness increases in the absence of Chinese aid.
@@
 Dreher et al.
-\citeyear{dreher2018} find that Chinese finance increases with Western development assistance, which they interpret as competitive behavior from China.
-Taken together, the literature seems to imply that there is some financial competition between the West and China that recipients may be able to take advantage of to procure more favorable borrowing terms.
-If recipients value better loan terms, including lower conditionality, and are willing to take on more debt, it follows that they should be attempting to stimulate this competition by diversifying their loan diet to include both Western and Chinese debt.
-While this logic stemming from the literature does not stipulate an exact proportion of Western finance to Chinese finance that optimizes recipient benefits, it should not be the case that countries borrow exclusively from one or the other.
-Interrogatively, do African countries at the center of this seeming financial competition borrow from the West and China at similar rates to benefit from their competition?
+(\citeyear{dreher2018}) find that Chinese finance increases with Western development assistance, which they interpret as competitive behavior from China (p.
+190).
+Taken together, the literature seems to imply that there is some financial competition between the West and China that recipients may be able to take advantage of to procure more favorable borrowing terms in the future.
+If recipients value better loan terms (i.e., lower conditionality) and are willing to take on more debt, it seems that it is optimal for recipients to borrow from both the West and China to stimulate competition and induce lower conditions from at least the West.
+While this logic stemming from the literature does not stipulate a precise proportion of Western to Chinese debt that optimizes recipient benefits, it should at least not be the case that countries borrow almost exclusively from one or the other.
+Interrogatively, do African countries borrow from the West and China in a way to benefit from their competition?
+Equivalently, do African countries have debt compositions largely comprised of both Chinese and Western loans?
 
 A cursory view of African debt suggests that this is not universally the case.
-The proportion of Chinese loans to Western loans varies substantially between counties and further that some countries almost entirely borrow from either China or the West when taking money from governments.
-For example, compare table 1 and table 2, which show the estimated composition of public debt in Cabo Verde and Djibouti, respectively (\cite{jubileedebtcampaign2018}).
-Cabo Verde owes only 1\% of its estimated total debt to China while debt to Portugal and other unspecified countries exceeds 25\%.
-In Djibouti, meanwhile, 68\% of its estimated debt can be attributed to China.
+The proportion of Chinese loans to Western loans varies substantially between counties and, further, some countries almost entirely borrow from either China or the West when taking money from governments.
+For example, according to information from a charity focused on alleviating debt across the world, the estimated composition of public debt in Cabo Verde and Djibouti nicely reflects this relative reliance on either the West or China (Table 1 and 2, \cite{jubileedebtcampaign2018}).
+Cabo Verde owes only 1\% of its estimated total debt to China while Djibouti can attribute 68\% of its estimated debt to China, by contrast.
 
@@
 
-Thus, the variance in debt composition and the seeming failure of countries to borrow in a more equal manner between China and Western entities must be explained.
-In other words, how do recipient countries decide between taking loans from China and the West?
-Taking loans is costly, at least in the long-run, and recipients presumably want to maximize the payoff they receive from borrowing.
-Related literature seems to not have fully considered recipient decision-making with regard to choosing a borrower, instead largely focusing on macroeconomic and political determinants of government debt (e.g., \cite{bittencourt2015} ; \cite{swamy2015}) or the determinants of lender behavior (e.g., \cite{dreher2018}).
+I gathered observational data from the World Bank (\cite{theworldbankgroup2022a}) and AidData (\cite{custer2021}) to look myself at the sum of loans received from both the World Bank and China for every African country from 2000-2017, as displayed in Table 3.
+I also provide information from the World Bank (\cite{theworldbankgroup2022}) on the public debt that each country carries.
+The table reveals a few apparent patterns.
+For one, World Bank loans seem to be much more common than those from China and, secondly, that the total amount of loans received from the World Bank is relatively constant across countries per a few exceptions (e.g., Namibia).
+Thirdly, there is extensive variation in the total amount of loans received from China.
+Some countries take none (e.g., Sao Tome and Principe), while others only consume Chinese finance relative to that from the World Bank (e.g., Equatorial Guinea).
+In conclusion, when focusing only on the World Bank and China, there is indication that some African countries take finance entirely from the West, others entirely from China, and others still borrow substantially from both (e.g., Botswana).
 
@@
 
+Thus, the variance in debt composition and seeming failure of countries to stimulate and benefit from competition by borrowing in a more equal manner between China and Western entities must be explained.
+In other words, why do some African countries almost exclusively borrow from either the West or China?
+While there may be little reason to suspect strategy in the reception of foreign aid and grants, it is more puzzling why countries may not optimize their costly loan intake.
+Recipients presumably want to minimize the costs associated with borrowing money.
+Related literature, though, seems to not have fully considered recipient decision-making with regard to choosing a borrower, instead largely focusing on macroeconomic and political determinants of government debt in general (e.g., \cite{bittencourt2015} ; \cite{swamy2015}) or the determinants of lender behavior (e.g., \cite{dreher2018}).
+
 \section*{My Explanation}
-I argue that the variation observed in African borrowing practices is a result of strategic considerations on behalf of recipients.
-Specifically, I argue that some countries take Chinese and Western finance at substantially different rates due to dissimilarities in the conditions of Western and Chinese loans and the subsequent evaluations of loan value by recipients.
+I argue that the variation observed in African borrowing practices is a result of strategic considerations on behalf of recipients, where countries borrow differently due to dissimilarities in the conditions of Western and Chinese loans and subsequent evaluations of loan value.
+Specifically, I argue that Western loans typically specify more political conditions and that, therefore, autocratic countries find it more preferable to borrow mostly from China despite the potential financial efficiency gains of incorporating more Western loans.
 
-There is evidence that China might be simultaneously more strict on the economic conditions on their finance (e.g., \cite{dreher2018}) while also less strict on the political conditions imposed (e.g., \cite{dreher2018}).
-Western loans, by contrast, seem more politically strict than economic (\cite{hernandez2017}).
-This dissimilarity leads to time-inconsistency problems, where in the short-term countries prefer either less severe economic or political conditions instead of minimizing the joint conditionality over the long-term.
+There is evidence to support the notion that conditionality differs between Chinese loans and those from the West.
+China seems simultaneously strict on economic conditions (e.g., \cite{dreher2018}; \cite{theeconomist2022}) while being more lax about the political conditions imposed (e.g., \cite{dreher2018}).
+Western loans, by contrast, seem at least equally strict on the political dimension versus the economic (\cite{hernandez2017}).
 
-%going back to the motivating example of Cabo Verde and Djibouti, these examples indeed fit this story as Cabo Verde is much more ``free'' than Djibouti, at least according to Freedom House
+All else equal ($ceteris\;paribus$), rational recipient countries should prefer to accept loans that have less strict conditions. %Why? What are some ways in which loan conditions are consequential?
+Further, $ceteris\;paribus$, more autocratic countries should prefer loans that attach fewer political conditions relative to their democratic counterparts.
+%Why?
+Be detailed.
+Usually entails liberal reforms.
+It should therefore be more costly for autocratic countries to accept loans from the West compared to democratic countries.
 
-One implication is that more democratic countries should be more sensitive to explicitly political conditions and, thus, prefer Western loans $ceteris\;paribus$.
-This could also explain Dreher et al.'s (\citeyear{dreher2018}) findings that Chinese loans seem to flow to more corrupt countries and those with poorer political institutions.
+I argue that, in the short term, this cost outweighs the expected benefit for autocrats of accepting more competitive Western loans and that, subsequently, autocratic countries should have a higher ratio of Chinese loans to those Western compared to democratic countries.
+This argument generates the following hypothesis:
+\begin{align*}
+    H_{1}&:\;\text{Autocracies have a higher ratio of Chinese loans to Western loans}\\
+\end{align*}
 
-\subsubsection*{Figure 1: Non-Democratic Country Loan Preference, $ceteris\;paribus$}
-\begin{tikzpicture}[scale=2,declare function={F(\x) = 1.7*(2*\x-\x*\x)-0.2;}]
-  \draw[-latex] (0,-0.2) -- (0,2) node[left]{$Utility$};
-  \draw[-latex] (-0.2,0) -- (2,0) node[below right]{$Political\;Conditionality$};
-  \draw[domain=0.1:1.9,samples=10,smooth,thick] plot (\x, {F(\x)}); 
-  \coordinate (max) at (0,{F(1)});
-  \draw[dashed] (max) -| (1,0) node[pos=1,below]{China};
-  \coordinate (max) at (0,{F(1.5)});
-  \draw[dashed] (max) -| (1.5,0) node[pos=1,below]{West};
-\end{tikzpicture}
+Anecdotally, this story fits with the motivating examples of Cabo Verde and Djibouti, who have Polity scores of 10 and 3 in 2020, respectively (\cite{marshall2018}).
+This explanation might also corroborate Dreher et al.'s (\citeyear{dreher2018}) finding that Chinese loans seem to flow to more corrupt countries and those with poorer political institutions.
 
 \section*{Research Design}
-The implication above leads to the following hypotheses:
-\begin{align*}
-    H_{1a}&:\;\text{Democracies should receive more Western loans than Chinese loans}\\
-    H_{1b}&:\;\text{Non-democracies should receive more Chinese loans than Western loans}\\
-\end{align*}
-To test these hypotheses I intend to focus on the international loan environment in Africa since from the years 2000 to 2020 due the continent being a major area of focus for China's finance projects and this being the time period most relevant for Chinese finance.
-I will fit a logit/probit model with the lender type (e.g., majority Western or not) as my dependent variable.
-The main explanatory variables will be regime type and a measure for loan conditionality.
-Ideally, an instrumental variable will be used for regime type since there is theoretically expected to be simultaneity present.
-Further, I will include gross domestic product (GDP) per capita as a control for recipient need and an additional control for the gross sum of the loan to ensure comparison.
+To test this hypothesis I collected observational data on all African countries from the years 2000 to 2017.
+This includes previously discussed data used for Table 3 (government debt, \cite{theworldbankgroup2022}; Chinese loans, \cite{custer2021}; and World Bank loans, \cite{theworldbankgroup2022a}), data on regime type from Polity (\cite{marshall2018}), and gross domestic product (GDP) per capita (\cite{unitednationsstatisticsdivision2019}).
+A summary of these variables can be found in Tables 4 and 5.
 
-I plan to use data from William \& Mary's ``Aiddata'' lab for Chinese loans (\cite{custer2021}) and data from the Organization for Economic Co-operation and Development (OECD) on Western loans (\cite{organizationforeconomicco-operationanddevelopment2022a}).
-GDP per capita stems from the United Nations (\cite{unitednationsstatisticsdivision2019}).
-For regime type, I intend to use an updated version of Cheibub et al.'s dictatorship and democracy index (\cite{cheibub2010}).
+To create a ratio of Chinese loans to Western loans, my dependent variable, I divided logged amounts of Chinese loans by logged amounts of loans from the World Bank.
+Values less than one for this variable indicate more World Bank loans than Chinese, while higher values than one indicate the opposite.
+Polity score is my main explanatory variable while GDP per capita is a potential confounder.
+I regressed this ratio on the Polity score and GDP per capita for each country in the sample, choosing a two-way fixed effects model after finding it superior to a pooled or random effects model.
+Clustered standard errors by country were also used.
+The results are presented in Table 6.
 
-\section*{Preliminary Analysis}
+\section*{Preliminary Results}
+The results suggest that GDP per capita is inversely related to the ratio of China loans to World Bank loans, implying that richer countries have smaller ratios of Chinese loans to World Bank loans.
+The main explanatory variable, Polity scores, is not significant at conventional levels, but does have the hypothesized sign (i.e., countries that are more autocratic and with lower Polity scores should be observed to have larger ratios of Chinese loans to World Bank loans).
+Therefore, there is no support for $H_1$ in the preliminary analysis.
 
@@
 
+\pagebreak
+\section*{Limitations and Future Improvements}
+There exist numerous improvements that must be made to this article.
+Theoretically, my proposed relationship is intimately related with time, though this is not yet operationalized in my hypothesis or fully included in the theoretical specification.
+I also need to develop more implications to empirically evaluate and discuss alternative explanations for the alleged unexplained observation of extreme debt composition variation.
+
+Empirically, I need to specify a better measure for the dependent variable.
+As it stands, the proposed ratio has two main drawbacks: Firstly, it does not have an upper-bound and thus over-emphasizes countries that receive more Chinese loans than Western loans (i.e., when World Bank loans are close to zero for a particular country, the ratio may go to infinity); Secondly, it only compares loans in single years, not across all the years observed.
+This means that a country can have a high ratio in a single year (i.e., more Chinese loans accepted than World Bank loans) but in reality have a low ratio over all years observed (i.e., in sum they accepted more World Bank loans than those from China).
+Further, there is an abundance of missing data for different measures that I need more time to deal with, perhaps via imputation.
+
+In addition, the main explanatory variable (Polity scores) does not have much variance across the years observed.
+Thus, it is not surprising that it does not account for much of the variation in the dependent variable (loan ratio), which itself has unnecessary variation built-in (since it can have extremely large values with comparatively little meaning).
+I would like to specify multiple measures of regime type and engage in numerous robustness checks for all variables.
+
 \section*{Discussion and Conclusion}
+While treated trivially in the past, I have argued that the evolving international financial competition in Africa has rendered recipient strategy an important question due to possible, unprecedented benefits they can receive from such competition.
+Autocracies, who find it more costly than democracies to take loans from the West due to traditionally high political conditions, continue to inefficiently diversify their debt composition between the West and China and do not actualize the potentially lower conditions that recent loan competition has induced.
+However, my early empirical results do not support the hypothesis that autocracies have larger loan ratios (i.e., China loans/World Bank loans) than democracies.
 
-\nocite{curini2020}
+Ideally, this article would be among the first to detail the importance of recipient behavior in the global finance literature.
+Understanding recipient behavior, instead of only engaging with the study of lenders and powerful countries, may shed light on the political and economic complexity unfolding in Africa and give clues to those concerned about the rising public debt occurring across the continent.
+Scholars must pay attention to the recipient motivations for accepting loans in addition to lenders' geopolitical motivations in offering them.
+
+I also contribute to the literature on the liberal international order (LIO), which is engaged in a debate on how China's recent prominence will affect the current LIO (e.g., \cite{weiss2021a}).
+China seems focused on increasing its global influence via growing its politico-economic ties with developing countries dissatisfied with the LIO (e.g., \cite{broz2020}), and understanding which developing countries have incentives to cooperate with China could be an important piece in calculating China's ability to build its influence and undermine the LIO, should that be what its true aim is.
+\nocite{leppert2021} \nocite{curini2020}
+
 \pagebreak
